Study of the hadronization of charged pions

### 2017-02-28 chap5.tex
Fixed figure link problems and add 120Sn statement

As the two experiments aimed at comparing deuterium with heavy nuclei, it was 
decided to use a double target system~\cite{Hakobyan:2008zz}. The first target 
was filled with liquid deuterium, and the second was a solid target. The 
latter was made of either carbon, aluminum, iron, tin or lead, and was changed 
remotely (see figure~\ref{fig:phototarget}). The two targets were separated by 
only 4~cm in order to minimize the difference on CLAS acceptance between them. 
The advantage of having two targets mounted simultaneously on the beam line is 
that several systematic effects related to the beam and detector properties 
cancel in the nuclear ratio.

@@

\begin{figure}[tbp]
\centering
\includegraphics[width=8cm] {answer-fig/TofProfile1.png} 
\caption {$\Delta \beta$ of positively charged particles for medium momentum slices 
(GeV/c). The red lines shows the applied cuts to select positive pions. The bump on the left
correspond to the kaon mass.}
\label{TOF-2}
\end{figure}

\begin{figure}[tbp]
\centering
\includegraphics[width=8cm] {answer-fig/TofProfile1.png} 
\caption {$\Delta \beta$ of positively charged particles for low momentum slices 
(GeV/c). The red lines shows the applied cuts to select positive pions. The bump on the left
correspond to the proton mass.}
\label{TOF-3}
\end{figure}

>>>>

As the two experiments aimed at comparing deuterium with heavy nuclei, it was 
decided to use a double target system~\cite{Hakobyan:2008zz}. The first target 
was filled with liquid deuterium, and the second was a solid target. The 
latter was made of either carbon, aluminum, iron, tin\footnote{The tin was 
enriched and composed of more than 99\% $^{120}$Sn.} or lead, and was changed 
remotely (see figure~\ref{fig:phototarget}). The two targets were separated by 
only 4~cm in order to minimize the difference on CLAS acceptance between them. 
The advantage of having two targets mounted simultaneously on the beam line is 
that several systematic effects related to the beam and detector properties 
cancel in the nuclear ratio.

@@

\begin{figure}[tbp]
\centering
\includegraphics[width=8cm] {answer-fig/TofProfile2.png} 
\caption {$\Delta \beta$ of positively charged particles for medium momentum slices 
(GeV/c). The red lines shows the applied cuts to select positive pions. The bump on the left
correspond to the kaon mass.}
\label{TOF-2}
\end{figure}

\begin{figure}[tbp]
\centering
\includegraphics[width=8cm] {answer-fig/TofProfile3.png} 
\caption {$\Delta \beta$ of positively charged particles for high momentum slices 
(GeV/c). The red lines shows the applied cuts to select positive pions. The bump on the left
correspond to the proton mass.}
\label{TOF-3}
\end{figure}
